Supporting Information

### 2017-02-09 code/rmarkdown/supporting-information.Rmd
update si and code

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap='insert caption here.'}
ggplot(benchmark.results.DF, aes(x=number.planning.units, y=time, color=number.features)) +
  geom_line() +
  facet_wrap(~ settings)
```

>>>>

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap='insert caption here.'}
plot(1)
```
